Dynamical dark energy constraints via clustering shells of SDSS-III BOSS galaxies

### 2017-06-22 Draft/Draft0.5.tex
minor changes

\title{\sffamily Dynamical dark energy constraints via clustering shells of SDSS-III BOSS galaxies}

\author{\sffamily 
Xiao-Dong Li,$^{1,\dagger}$
Cristiano G. Sabiu,$^{2}$
Changbom Park,$^{1}$
Yuting Wang,$^{3,\star}$
Gong-bo Zhao,$^{3}$
Hyunbae Park,$^{2}$
Arman Shafieloo,$^{2}$
Juhan Kim,$^{4,1}$
and Sungwook E. Hong$^{2}$}
%Enrico Corsaro$^{1,2,3,4}$, Yueh-Ning Lee$^1$, Rafael A. Garc\'{i}a$^{1}$, Patrick Hennebelle$^1$, Savita Mathur$^{5}$, Paul G. Beck$^1$, Stephane Mathis$^1$, Dennis Stello$^{6,7}$ \& J\'er\^{o}me Bouvier$^8$}

@@

\vspace{-3.5mm}
\begin{abstract}
\sffamily
We use the anisotropic {\it clustering shells} of 1,133,326 galaxies from the Sloan Digital Sky Survey Data Release 
12 spanning the redshift range $0.15<z<0.69$ to place constraints on the expansion history of the Universe. 
Concentrating on the Chevallier-Polarski-Linder parametrization of dark energy $w=w_0+w_a\frac{z}{1+z}$,
while improving upon earlier works \citep{Li2016}, 
we present a novel use of the Alcock-Paczynski (AP) test via the small scales clustering difference between redshift bins. 
This differential measure appears to be a robust statistical tool which mitigates many systematic effects, 
allowing for competitive and unbiased constrains. 
A combination of CMB+BAO+SNIa+$H_0$+AP yields
$\Omega_m = 0.301 \pm 0.008,\ w_0 = -1.042 \pm 0.067,\ w_a = -0.07 \pm 0.29$ (68.3\% CL).
Adding the AP method reduces the $w_0-w_a$ contour area by 50\%.
The method can be combined with the standard BAO method, 
increasing the science output of ongoing and future galaxy surveys by a factor of 2.
\end{abstract}

\sffamily
{\it Introduction.}---
The  origin  of  the  accelerating  expansion  of  the  universe  is  one of  the  most  salient  questions  in  contemporary cosmology. 
Proposed mechanisms include  evolving  scalar  fields  remnant  from  the  big  bang, 
modifications to gravity,  and a  non-zero  vacuum energy \cite[see][for a comprehensive review]{2012IJMPD..2130002Y}. 
Considering the wealth of theoretical explanations, it is crucial to obtain precise and unbiased measurements of the expansion history of the Universe allowing us to 
differentiate between competing dark energy models.

@@

The main caveat of the AP test is due to the fact that 
the radial distances of galaxies are inferred from observed redshifts.
Thus AP tests are inevitably affected by peculiar motions of galaxies,
which leads to apparent anisotropy in the clustering signal, even if the adopted cosmology is correct.
The effect, known as redshift-space distortions (RSD),
is notoriously difficult to model accurately in the 2-point statistics of galaxy clustering \citep{Ballinger1996}.

As alternative methods, \cite{Marinoni2010} proposed using the symmetry properties of galaxy pairs;
however, since the peculiar velocity distorts the redshifts and changes the apparent tilt angles of galaxy pairs,
this method is also seriously limited by RSD \citep{Jennings2011}.
\cite{Ryden1995} and \cite{LavausWandelt1995} proposed another method using the apparent stretching of voids.
This approach has the advantage that the void regions are easier to model compared with dense regions,
but has limitations in that it utilizes only low density regions of the LSS and requires large samples to achieve competitive constraints \citep{Qingqing2016}.

@@

In an effort to mitigate the RSD effect, \cite{Li2014} proposed utilizing the {\it redshift dependence} of the AP effect. 
The clustering anisotropies produced by are, although large, close to uniform in magnitude over a wide range in redshift. 
However, if cosmological parameters are incorrectly chosen resulting in an AP effect, 
the anisotropy in the clustering signal has a clear redshift dependence. 
In a later work, \cite{Li2015} developed an AP methodology 
that utilises the redshift dependence of the galaxy 2-point correlation function (2pCF), 
measured as a function of angle between the galaxy pair and line-of-sight (LoS).
As an illustration, Fig.\ref{fig_xy} shows how the shape distortion of objects (anisotropy of clustering signal) varies with distance (or redshift) when incorrect values of  $w_0$ or $w_a$ are used to infer distances.

\citep{Li2016} applied their AP method to galaxies from the 3rd incarnation of the Sloan Digital Sky Survey (SDSS-III).
Combining their method with measurements of the Cosmic Microwave Background (CMB), type Ia supernovae (SNIa), 
baryon acoustic oscillations (BAO), and $H_0$,
they obtained very tight constraints of $ \Omega_m = 0.301 \pm 0.006,\ w=-1.054 \pm 0.025$.
In reducing the RSD effect, 
they were able to use galaxy clustering on scales down to 6 $h^{-1}$Mpc,
which is a major advance in extracting cosmological information 
on small scales where galaxy clustering is strong and there are many independent structures.

In this paper, we continue to develop our previous methodology and proceed to infer the constraints on dynamical dark energy. 
We will present a slightly improved methodology to that of \citep{Li2016}, 
allowing for faster likelihood estimation and thus the exploration of larger, higher dimensional parameter spaces. 
The methodology we will present here, can be applied to any model of dynamical dark energy, 
or indeed any appropriately chosen parametric or non-parametric decomposition of the cosmic expansion history. 
However, as a first step, in this paper we will focus on the widely used Chevallier-Polarski-Linder (CPL) parametrization
$w(z) = w_0 + w_a \frac{z}{1+z}$.

The Planck team has released the {\texttt {COSMOMC}} \citep{LB2002} outputs of four MCMC ``chains'' in the CPL model, 
using a combination of four datasets:
the full-mission Planck observations of CMB temperature and polarization anisotropies \cite{Planck2015},
the BAO distance priors measured from SDSS DR11 \citep{Anderson2013}, 6dFGS \citep{6dFGS} and SDSS MGS \citep{MGS},
the ``JLA'' SNIa sample \citep{JLA},
and the Hubble Space Telescope measurement of $H_0=70.6\pm3.3$ \cite{Riess2011,E14H0}.
These MCMC chains contain the CMB+BAO+SNIa+$H_0$ likelihood computed for $\sim$37,000 sets of cosmological parameters,
yielding constraints of 
\begin{equation}
 \Omega_m = 0.309 \pm 0.010, w_0 = -0.938 \pm 0.109, w_a = -0.38 \pm 0.41.
\end{equation}
%To include the AP method into the constraints,
We then compute the likelihood of the LOWZ+CMASS AP measurements for each of the parameter combinations provided in the Planck chain. 
To do this, we splited the 1,133,326 galaxies from the SDSS DR12 into six redshift bins,
measured the 2pCF in these redshift bins, 
and use a $\chi^2$ function to assess the redshift dependence.
Systematic effects are estimated via mocks made from Horizon Run 4 simulations \citep{HR4}, and subtracted when computing the $\chi^2$.
After adding the sample log-likelihoods with ours, 
while also multiply the sample weights by our likelihoods, 
we derive the CMB+BAO+SNIa+$H_0$+AP constraints on CPL parameters,
\begin{equation}
%\Omega_m = 0.300 \pm 0.008, w_0 = -1.056 \pm 0.061, w_a = -0.04 \pm 0.27,
    %1  0.2999656E+00  0.7616334E-02  0.2958745E+00  0.3035033E+00  0.2878169E+00  0.3132870E+00   \Omega_m
    %2  0.6904801E+00  0.8675444E-02  0.6808558E+00  0.6993898E+00  0.6722945E+00  0.7052207E+00   h
    %3 -0.1056468E+01  0.6096323E-01 -0.1116874E+01 -0.9965903E+00 -0.1175041E+01 -0.9287388E+00   w
    %4 -0.3808376E-01  0.2716607E+00 -0.3105235E+00  0.2321461E+00 -0.6033103E+00  0.4782076E+00   w_a    
\Omega_m = 0.301 \pm 0.008, w_0 = -1.042 \pm 0.067, w_a = -0.07 \pm 0.29.
%    1  0.3014353E+00  0.7759923E-02  0.2974325E+00  0.3048882E+00  0.2889838E+00  0.3152269E+00   \Omega_m
%    2  0.6887652E+00  0.8760036E-02  0.6797134E+00  0.6978279E+00  0.6703971E+00  0.7044224E+00   h
%    3 -0.1041626E+01  0.6732817E-01 -0.1107730E+01 -0.9768319E+00 -0.1172149E+01 -0.8979017E+00   w
%    4 -0.7173374E-01  0.2860547E+00 -0.3572176E+00  0.2107347E+00 -0.6775045E+00  0.4558817E+00   w_a    
\end{equation}
%$$.
While the central values of parameters do not shift appreciably,
the error bars of $w_0$ and $w_a$ are reduced by 38.4\% and 29.7\%, respectively.% $$-40\%$ by adding our method into the analysis.

@@

The derived cosmological constraints are fully consistent with a cosmological constant dark energy component having no evolution.
Adding the new AP method to the CMB+BAO+SNIa+$H_0$ constraints reduces the statistical errors by $\sim$30-40\%,
and reduces the 95.4\% CL $w_0-w_a$ contour by 50\%.
This reveals the constraining power of the small scale AP effect for probing the redshift evolution of dark energy.

We performed a thorough test of all the possible variables in our methodology.
Figure \ref{fig_contest} shows that,
the result does not change if change them.
%we adopt $\mu_{\rm max}=0.99\ (0.85)$ to include more (less) regions near the LOS,
%decrease the number of angular bins to $n_{\mu}=15-20$,
%change the range of clustering to $8-30 \rm Mpc/h$,
%change the fiducial cosmology to $\Omega_m=0.26,\ w=-0.6$,
%exclude 1 or 2 high redshift bins,
%or reduce the number of mocks to 1000.
The most striking point to note in our testing is that the 
shift in contour position is very small even when we do not include the systematic correction.
This is reassuring, since we may have worried that {\it cosmological dependence} 
on the systematic correction could influence on our final results.

In sum, \cite{Li2016} proposed to constrain cosmological parameters via 
the redshift dependence of galaxy anisotropic clustering.
This enables a robust AP test on relatively small scales.
In this paper we improved the methodology and obtained tight constraints on the CPL parametrization of dark energy.
%using 1,133,326 galaxies from the Sloan Digital Sky Survey Data Release 
%12 spanning the redshift range $0.15<z<0.69$ . 
%Adding our constraints to the CMB+SNIa+BAO+$H_0$ combination, the $w_0-w_a$ contour was reduced by $\sim50$\%.
The AP method presented in this work has many advantages over the `traditional' galaxy clustering method.
Since it works with the redshift evolution of the anisotropic clustering signal it significantly reduces the effect of systematics. 
It avoids the great difficulty in accurate modelling of the RSD, non-linear clustering and galaxy bias.
It is applicable on much smaller scales, allowing for the inclusion of more $k$-modes and hence more information.

The presented method of clustering shells can be applied to many spectroscopic galaxy surveys. 
The method is complimentary to the BAO method and the two methods can be combined together, 
increasing (by roughly twice) the science output of ongoing and future surveys, with little to no additional cost.
We expect it play an important role in helping us unveiling the mystery of dark energy.

@@

\bibitem[Ade et al. (2015)]{Planck2015}
Ade, P.A.R., Aghanim, N., \& Arnaud, M., et al. arXiv:1502.01589

\bibitem[Alam et al.(2016)]{Alam2016}
Alam, S., Ata, M., \& Bailey, S., et al. 2016,
submitted to MNRAS (arXiv:1607.03155)

%\bibitem[{{Alam} {et~al}\mbox{.}(2015{\natexlab{a}}){Alam}, {Albareti},
%  {Allende Prieto}, {Anders}, {Anderson}, {Anderton}, {Andrews}, {Armengaud},
%  {Aubourg}, {Bailey}, \& et~al.}]{dr12}
%{Alam} S., Albareti, F.D.,\& Allende Prieto, C., {et~al.}, 2015,  ApJS, 219, 12

\bibitem[Alcock \& Paczynski(1979)]{AP1979}
Alcock, C., \& Paczynski, B. 1979, Nature, 281, 358

%\bibitem[Anderson et al.(2012)]{2012MNRAS.427.3435A} 
%Anderson, L., Aubourg, E., Bailey, S., et al.\ 2012, MNRAS, 427, 3435

\bibitem[Anderson et al.(2013)]{Anderson2013}
Anderson, L., Aubourg, \'E., \& Bailey, S. et al. 2014, MNRAS, 441, 24

%\bibitem[Bassett et al.(2002)]{Bassett2002}
%Bassett, B.A., Kunz, M., Silk, J., \& Ungarelli, C. 2002, MNRAS, 336, 1217

\bibitem[Ballinger, Peacock \& Heavens 1996]{Ballinger1996}
Ballinger, W.E., Peacock, J.A., \& Heavens, A.F. 1996, MNRAS, 282, 877

\bibitem[Betoule et al.(2014)]{JLA}
Betoule, M., Kessler, R., \& Guy, J., et al. 2014, A\&A, 568, 32

\bibitem[Beutler et al.(2011)]{6dFGS}
Beutler, F., Blake, C., \& Colless, M., et al. 2011, MNRAS, 416, 3017

\bibitem[Beutler et al.(2013)]{Beutler2013}
Beutler, F., Saito, S., \& Seo, H.-J., et al. 2013, MNRAS, 443, 1065

\bibitem[Beutler et al.(2016)]{Beutler2016}
Beutler, F., Seo, H.-J., \& Saito, S., et al. 2016,
arXiv:1607.03150

\bibitem[Blake et al.(2011)]{Blake2011}
Blake, C., Glazebrook, K., \& Davis, T. M., 2011, MNRAS, 418, 1725

\bibitem[Blake et al.(2013)]{WiggleZtopoloy}
Blake, C., James, J.B., \& Poole, G.B. 2013, MNRAS, 437, 2488

\bibitem[Bolton et al.(2012)]{Bolton2012}
Bolton, A.S., Schlegel, \& D.J., Aubourg E., et al. 2012, AJ, 144, 144

\bibitem[Boylan-Kolchin et al.(2008)]{B08}
Boylan-Kolchin, M., Ma, C.-P., \& Quataert, E. 2008, MNRAS, 383, 93

%\bibitem[Bueno Belloso et al. (2012)]{BB2012}
%Bueno Belloso, A., Pettinari, G.W., Meures, N., \& Percival, W.J. 2012, Phys. Rev. D, 86, 023530

%\bibitem[Chevallier \& Polarski(2001)]{CP2001}
%Chevallier, M., Polarski, D. 2001, Int. J. Mod. Phys. D, 10, 213

%\bibitem[Choi et al.(2010)]{choi 2010}
%Choi, Y.-Y., Park, C., Kim, J., Gott, J.R., 
%Weinberg, D.H., Vogeley, M.S., \& Kim, S.S. 2010, ApJS, 190, 181

\bibitem[Christensen et al.(2001)]{Bayesian}
Christensen, N., Meyer, R., Knox, L., \& Luey, B. 2001, Class. Quant. Grav., 18, 2677

%\bibitem[Chuang et al.(2013)]{Chuang2013}
%Chuang, C.-H., Prada, F., Beutler, F., et al. 2013, arXiv:1312.4889

\bibitem[Chuang \& Wang(2012)]{ChuangWang2012}
Chuang, C.-H., \& Wang, Y. 2012, MNRAS, 426, 226

%\bibitem[Corasaniti \& Copeland(2003)]{Corasaniti2003}
%Corasaniti, P.S., Copeland, E.J. 2003, Phys. Rev. D, 67, 063521

%eBOSS: 
%http://arxiv.org/abs/1508.04473
\bibitem[Dawson et al.(2015)]{eBOSS}
Dawson, K.S., Kneib, J.P., \& Percival, W.J., et al. 2015, accepted AJ

\bibitem[Dawson et al.(2012)]{Dawson et al. 2012}
Dawson, K.S., Schlegel, D.J., \& Ahn, C.P., et al. 2012, AJ, 145, 10

\bibitem[Efstathiou (2014)]{E14H0}
Efstathiou, G. 2014, MNRAS, 440, 1138

\bibitem[Eisenstein et al.(2011)]{Eisenstein et al. 2011}
Eisenstein, D.J.,  Weinberg, D.H., \& Agolet, E., et al. 2011, AJ, 142, 72

\bibitem[Feldman, Kaiser \& Peacock (1994)]{1994ApJ...426...23F} 
Feldman, H.A., Kaiser, N., \& Peacock, J.A.\ 1994, ApJ, 426, 23

\bibitem[Fukugita et al. (1996)]{Fukugita1996}
Fukugita, M., Ichikawa, T., \& Gunn, J.E., et al. 1996, AJ, 111, 1748
%Publication:	
%Astronomical Journal v.111, p.1748

%\bibitem[Gingold \& Monaghan(1977)]{GM1977}
%Gingold, R.A., \& Monaghan, J.J. 1977, MNRAS, 181, 375

%\bibitem[Gott et al.(2009)]{gott 2009}
%Gott, J.R., Choi, Y.-Y., Park, C., \& Kim, J. 2009, ApJ, 695, L45

%\bibitem[Gott et al.(2008)]{gott 2008}
%Gott, J.R., Hambrick, D.C., Vogeley, M.S., Kim, J., Park, C., Choi, Y.-Y.,
%Cen, R., Ostriker, J.P., \& Nagamine, K. 2008, ApJ, 675, 16

\bibitem[Gunn et al. (1998)]{Gunn1998}	
Gunn, J.E., Carr, M., \& Rockosi, C. et al. 1998, AJ, 116, 3040

\bibitem[Gunn et al.(2006)]{Gunn et al. 2006}
Gunn, J.E., Siegmund, W.A., \& Mannery, E.J., et al. 2006, AJ, 131, 2332

\bibitem[Guzzo et al.(2008)]{Guzzo2008}
Guzzo, L., Pierleoni, M., \& Meneux, B., et al. 2008, Nature, 451, 541

\bibitem[Hartlap et al.(2006)]{Hartlap}
Hartlap J., Simon P. \& Schneider P. [astro-ph/0608064].

\bibitem[Hong et al.(2016)]{hong2016}
Hong, S.E., Park, C.,\&  Kim, J. 2016, ApJ, 823, 103

\bibitem[Jackson (1972)]{FOG}
Jackson, J., 1972, MNRAS, 156, 1

\bibitem[Jennings et al.(2011)]{Jennings2011}
Jennings, E., Baugh, C.M., \& Pascoli, S. 2011, MNRAS, 420, 1079

%\bibitem[Jeong et al.(2014)]{Jeong2014}
%Jeong, D., Dai, L., Kamionkowski, M., \& Szalay, A.S. 2014, arXiv:1408.4648

\bibitem[Jiang et al.(2008)]{jiang2008}
Jiang, C.Y., Jing, Y. P., \& Faltenbacher, A., et al. 2008, ApJ, 675, 1095

\bibitem[Kaiser (1987)]{Kaiser1987}
Kaiser, N. 1987, MNRAS, 227, 1

\bibitem[Kim \& Park(2006)]{kim and park 2006}
Kim, J., \& Park, C. 2006, ApJ, 639, 600

\bibitem[Kim et al.(2009)]{2009ApJ...701.1547K} 
Kim, J., Park, C., Gott, J.R., III, \& Dubinski, J.\ 2009, ApJ, 701, 1547

\bibitem[Kim et al.(2015)]{hr4}
Kim, J., Park, C., L'Huillier, B., \& Hong, S. E. 2015, JKAS, 48, 213

\bibitem[Kim et al.(2011)]{horizonrun}
Kim, J., Park, C., Rossi, G., Lee, S.M., \& Gott, J.R. 2011, JKAS, 44, 217

\bibitem[Kitaura et al.(2015)]{MDPATCHY}
Kitaura, F.S., Rodriguez-Torres, S., Chuang, C.-H., et al. arXiv:1509.06400

\bibitem[Komatsu et al.(2011)]{komatsu 2011}
Komatsu, E., Smith, K. M., \& Dunkley, J., et al. 2011, ApJS, 192, 18

\bibitem[Lacey \& Cole(1993)]{LC93}
Lacey, C., \& Cole, S. 1993, MNRAS, 262, 627

\bibitem[Landy \& Szalay(1993)]{1993ApJ...412...64L} 
Landy, S.D., \& Szalay, A.S.\ 1993, ApJ, 412, 64

%EUCLID:
%http://arxiv.org/abs/1110.3193
\bibitem[Laureijs et al.(2011)]{EUCLID}
Laureijs, R., Amiaux, J., \& Arduini, S., et al. 2011, arXiv:1110.3193

\bibitem[Lavaux \& Wandelt(2012)]{LavausWandelt1995}
Lavaux, G., \& Wandelt, B.D. 2012, ApJ, 754, 109

%\bibitem[Levi et al.(2013)]{2013arXiv1308.0847L} 
%Levi, M., Bebek, C., Beers, T., et al.\ 2013, arXiv:1308.0847

>>>>

\title{%\sffamily 
Dynamical dark energy constraints via clustering shells of SDSS-III BOSS galaxies}
\title{%\sffamily 
Constraints on the cosmic expansion history using the small scale clustering of SDSS-III BOSS galaxies}

\author{%\sffamily 
Xiao-Dong Li,$^{1}$
Cristiano G. Sabiu,$^{2}$
Changbom Park,$^{1}$
Yuting Wang,$^{3}$
Gong-bo Zhao,$^{3}$
Hyunbae Park,$^{2}$
Arman Shafieloo,$^{2}$
Juhan Kim,$^{4,1}$
and Sungwook E. Hong$^{2}$}

@@

\vspace{-3.5mm}
\begin{abstract}
%\sffamily
We use the small scale anisotropic clustering signal of 1,133,326 galaxies from the Sloan Digital Sky Survey Data Release 
12, spanning the redshift range $0.15<z<0.69$ to place constraints on the expansion history of the Universe. 
Concentrating on the Chevallier-Polarski-Linder parametrization of dark energy, $w=w_0+w_a\frac{z}{1+z}$,
while improving upon earlier works \citep{Li2016}, 
we present a novel use of the Alcock-Paczynski (AP) test via the small scales clustering difference between redshift bins. 
This differential measure is shown to be a robust statistical tool that mitigates many systematic effects, 
allowing for competitive and unbiased constrains to be placed on cosmological parameters.
We find that our results, in combination with the CMB, BAO, SNIa and $H_0$ from Cepheid data yield, 
$\Omega_m = 0.301 \pm 0.008,\ w_0 = -1.042 \pm 0.067,\ w_a = -0.07 \pm 0.29$ (68.3\% CL). 
Adding our new AP measurements to the aforementioned results reduced the $w_0-w_a$ 1-$\sigma$ contour area by 50\%.
The AP method can be combined with the standard BAO method, 
increasing the science output of ongoing and future galaxy surveys by a factor of 2.
\end{abstract}

%\sffamily
%{\it Introduction.}---
The  origin  of  the late-time accelerating  expansion  of  the  universe  is  one of  the  most  salient  questions  in  contemporary cosmology. Theoretical explanations for this phenomena are many and range from a non-zero  vacuum energy and evolving  scalar  fields  remnant  from  the  big  bang, to modifications of Einstein's General Relativity\cite{2012IJMPD..2130002Y}. 
Considering the wealth of theoretical explanations, it is crucial to obtain precise and unbiased measurements of the expansion history of the Universe allowing us to 
differentiate between competing models.

@@

The main caveat in applying the AP test is due to the fact that 
the radial distances of galaxies are inferred from observed redshifts.
Thus AP tests are inevitably affected by peculiar the motions of galaxies,
which leads to apparent anisotropy in the clustering signal, even if the adopted cosmology is correct.
The effect, known as redshift-space distortions (RSD),
is notoriously difficult to model accurately in the statistics of galaxy clustering \citep{Ballinger1996}.

The symmetry properties of galaxy pairs\cite{Marinoni2010}  could also be used to probe the AP effect;
however, since the peculiar velocity distorts the redshifts and changes the apparent tilt angles of galaxy pairs,
this method is also seriously limited by RSD \citep{Jennings2011}.

In an effort to minimise RSD contamination, the shape of void regions\cite{Ryden1995,LavausWandelt1995}  has been 
proposed as an AP probe. This approach has the advantage that the void regions are easier to model compared with dense regions, but has limitations in that it utilizes only low density regions of the LSS and requires large samples to achieve competitive constraints \citep{Qingqing2016}.

@@

Previously, we proposed to use the  {\it redshift dependence} of the AP distortion\cite{Li2014} as a way of mitigating the RSD effect. The clustering anisotropies produced by RSD are, although large, close to uniform in magnitude over a wide range in redshift.  However, if cosmological parameters are incorrectly chosen resulting in an AP effect, 
the anisotropy in the clustering signal has a clear redshift dependence. 
In a later work\cite{Li2015}, we developed an AP methodology 
that utilises the redshift dependence of the galaxy 2-point correlation function (2pCF), 
measured as a function of angle between the galaxy pair and line-of-sight (LoS).
As an illustration, Fig.\ref{fig_xy} shows how the shape distortion of objects (anisotropy of clustering signal) varies with distance (or redshift) when incorrect values of  $w_0$ or $w_a$ are used to infer distances.

In earlier work\citep{Li2016} we applied this AP method to galaxies from the 3rd incarnation of the Sloan Digital Sky Survey (SDSS-III). Combining their method with measurements of the Cosmic Microwave Background (CMB), type Ia supernovae (SNIa), 
baryon acoustic oscillations (BAO), and $H_0$,
they obtained very tight constraints of $ \Omega_m = 0.301 \pm 0.006,\ w=-1.054 \pm 0.025$.
In reducing the RSD effect, 
they were able to use galaxy clustering on scales down to 6 $h^{-1}$Mpc,
which is a major advance in extracting cosmological information 
on small scales where galaxy clustering is strong and there are many independent structures.

In this paper, we continue to develop our previous methodology and proceed to infer the constraints on dynamical dark energy. 
We will present a slightly improved methodology to that of our previous work\citep{Li2016}, 
allowing for faster likelihood estimation and thus the exploration of larger, higher dimensional parameter spaces. 
The methodology we will present here, can be applied to any model of dynamical dark energy, 
or indeed any appropriately chosen parametric or non-parametric decomposition of the cosmic expansion history. 
However, as a first step, in this paper we will focus on the widely used Chevallier-Polarski-Linder (CPL) parametrization
$w(z) = w_0 + w_a \frac{z}{1+z}$.

The Planck team has released the {\texttt {COSMOMC}} \citep{LB2002} outputs of four MCMC ``chains'' in the CPL model, 
using a combination of four datasets:
the full-mission Planck observations of CMB temperature and polarization anisotropies \cite{Planck2015},
the BAO distance priors measured from SDSS DR11 \citep{Anderson2013}, 6dFGS \citep{6dFGS} and SDSS MGS \citep{MGS},
the ``JLA'' SNIa sample \citep{JLA},
and the Hubble Space Telescope measurement of $H_0=70.6\pm3.3$ \cite{Riess2011,E14H0}.
These MCMC chains contain the CMB+BAO+SNIa+$H_0$ likelihood computed for $\sim$37,000 sets of cosmological parameters,
yielding constraints of $ \Omega_m = 0.309 \pm 0.010, w_0 = -0.938 \pm 0.109, w_a = -0.38 \pm 0.41$.
%\begin{equation}
 %\Omega_m = 0.309 \pm 0.010, w_0 = -0.938 \pm 0.109, w_a = -0.38 \pm 0.41.
%end{equation}
We then compute the likelihood of the LOWZ+CMASS AP measurements for each of the parameter combinations provided in the Planck chain. 
To do this, we splited the 1,133,326 galaxies from the SDSS DR12 into six redshift bins,
measured the 2pCF in these redshift bins, 
subtract the systematic effects based on estimations from mocks made from Horizon Run 4 simulations \citep{HR4},
and use a $\chi^2$ function to assess the redshift dependence
(see Methods for further explanations).
After adding the sample log-likelihoods with ours, 
while also multiply the sample weights by our likelihoods, 
we derive the CMB+BAO+SNIa+$H_0$+AP constraints on CPL parameters, $\Omega_m = 0.301 \pm 0.008, w_0 = -1.042 \pm 0.067, w_a = -0.07 \pm 0.29$.
%\begin{equation}
%\Omega_m = 0.301 \pm 0.008, w_0 = -1.042 \pm 0.067, w_a = -0.07 \pm 0.29.
%\end{equation}
While the central values of parameters do not shift appreciably,
the error bars of $w_0$ and $w_a$ are reduced by 38.4\% and 29.7\%, respectively.% $$-40\%$ by adding our method into the analysis.

@@

The derived cosmological constraints are fully consistent with a cosmological constant dark energy component having no evolution.
Adding the new AP method to the CMB+BAO+SNIa+$H_0$ constraints reduces the statistical errors on many parameters by $\sim$30-40\% and reduces the $w_0-w_a$  (95.4\% CL) contour by 50\%.
This reveals the constraining power of the small scale AP effect for probing the redshift evolution of dark energy.

We performed a thorough test of all the possible variables in our methodology.
Figure \ref{fig_contest} shows that 
the result is unaffected by the line-of-sight $\mu$-cut, the number of angular bins, the range of radial integration and the choice of fiducial cosmology. 
%we adopt $\mu_{\rm max}=0.99\ (0.85)$ to include more (less) regions near the LOS,
%decrease the number of angular bins to $n_{\mu}=15-20$,
%change the range of clustering to $8-30 \rm Mpc/h$,
%change the fiducial cosmology to $\Omega_m=0.26,\ w=-0.6$,
%exclude 1 or 2 high redshift bins,
%or reduce the number of mocks to 1000.
The most striking point to note in our testing is that the 
shift in contour position is very small even when we do not include the systematic correction.
This is reassuring, since we may have worried that {\it cosmological dependence} 
of the systematic correction could influence the final result.

In summary, we previously proposed to constrain cosmological parameters via 
the redshift dependence of anisotropic galaxy clustering\cite{Li2016}.
This approach enables a robust AP test on relatively small scales.
In this paper we improved the methodology and obtained tight constraints on the CPL parametrization of dark energy.
%using 1,133,326 galaxies from the Sloan Digital Sky Survey Data Release 
%12 spanning the redshift range $0.15<z<0.69$ . 
%Adding our constraints to the CMB+SNIa+BAO+$H_0$ combination, the $w_0-w_a$ contour was reduced by $\sim50$\%.
The AP method presented in this work has many advantages over the `traditional' galaxy clustering method.
Since it works with the redshift evolution of the anisotropic clustering signal it significantly reduces the effect of systematics. 
It avoids the great difficulty in accurate modelling of the RSD, non-linear clustering and galaxy bias.
It is applicable on much smaller scales, allowing for the inclusion of more $k$-modes and hence more information.

The presented method of clustering shells can be applied to many spectroscopic galaxy surveys. 
The method is complimentary to the BAO method and the two methods can be combined together, 
increasing (by roughly twice) the science output of ongoing and future surveys, with little to no additional cost.
We expect this approach will play an important role in helping us unveiling the mystery of dark energy.

@@

\bibitem{Li2016}%[Li et al.(2016)]
Li, X.-D., Park, C., \& Sabiu, C.G., et al. 2016, ApJ, 832, 103

\bibitem{2012IJMPD..2130002Y}%[Yoo \& Watanabe(2012)]
Yoo, J., \& Watanabe, Y.\ 2012, International Journal of Modern Physics D, 21, 1230002

\bibitem{AP1979}%[Alcock \& Paczynski(1979)]
Alcock, C., \& Paczynski, B. 1979, Nature, 281, 358

\bibitem{Outram2004}%[Outram et al.(2004)]
Outram, P.J., Shanks, T., Boyle, B.J., Croom, S.M., Hoyle, F., Loaring, N.S., 
Miller, L., \& Smith, R.J. 2004, MNRAS, 348, 745

\bibitem{Blake2011}%[Blake et al.(2011)]
Blake, C., Glazebrook, K., \& Davis, T. M., 2011, MNRAS, 418, 1725

\bibitem{Alam2016}%[Alam et al.(2016)]
Alam, S., Ata, M., \& Bailey, S., et al. 2016,
submitted to MNRAS (arXiv:1607.03155)

\bibitem{Ballinger1996}%[Ballinger, Peacock \& Heavens 1996]
Ballinger, W.E., Peacock, J.A., \& Heavens, A.F. 1996, MNRAS, 282, 877

\bibitem{Marinoni2010}%[Marinoni \& Buzzi(2010)]
Marinoni, C., \& Buzzi, A. 2010, Nature, 468, 539

\bibitem{Jennings2011}%[Jennings et al.(2011)]
Jennings, E., Baugh, C.M., \& Pascoli, S. 2011, MNRAS, 420, 1079

\bibitem{Ryden1995}%[Ryden(1995)]
Ryden, B.S. 1995, ApJ, 452, 25

\bibitem{LavausWandelt1995}%[Lavaux \& Wandelt(2012)]
Lavaux, G., \& Wandelt, B.D. 2012, ApJ, 754, 109

\bibitem{Qingqing2016}%[Mao et al. (2016)]
Mao, Q., Berlind, A.A., Scherrer, R.J., et al. 2016, submitted to ApJ

\bibitem{Li2014}%[Li et al.(2014)]
Li, X.-D., Park, C., Forero-Romero, J., \& Kim, J. 2014, ApJ, 796, 137

\bibitem{Li2015}%[Li et al.(2015)]
Li, X.-D., Park, C., Sabiu, C.G., \& Kim, J. 2015, MNRAS, 450, 807

\bibitem{LB2002}%[Lewis \& Bridle (2002)]
Lewis, A., \& Bridle, S. 2002, Phys. Rev. D, 66, 103511

\bibitem{Planck2015}%[Ade et al. (2015)]
Ade, P.A.R., Aghanim, N., \& Arnaud, M., et al. 2016, A\&A, 594, A13

\bibitem{Anderson2013}%[Anderson et al.(2013)]
Anderson, L., Aubourg, \'E., \& Bailey, S. et al. 2014, MNRAS, 441, 24

\bibitem{6dFGS}%[Beutler et al.(2011)]
Beutler, F., Blake, C., \& Colless, M., et al. 2011, MNRAS, 416, 3017

\bibitem{MGS}%[Ross et al.(2015)]
Ross, A.J., Samushia, L., \& Howlett, C., et al. 2015, MNRAS, 449, 835

\bibitem{JLA}%[Betoule et al.(2014)]
Betoule, M., Kessler, R., \& Guy, J., et al. 2014, A\&A, 568, 32

\bibitem{Riess2011}%[Riess et al.(2011)]
Riess, A.G., Macri, L., \& Casertano, S., et al. 2011, ApJ, 730, 119

\bibitem{E14H0}%[Efstathiou (2014)]
Efstathiou, G. 2014, MNRAS, 440, 1138

\bibitem{HR4}%[Kim et al.(2015)]
Kim, J., Park, C., L'Huillier, B., \& Hong, S. E. 2015, JKAS, 48, 213

%\bibitem{Lee12}
%\bibinfo{author}{Lee}, E.~J., {Murray}, N., {Rahman}, M. 
%\newblock \bibinfo{title}{Milky Way Star-forming Complexes and the Turbulent Motion of the Galaxy's Molecular Gas.}
%\newblock{\it Astrophys. \ J.}{\bf\, 752}, 146-159 (2012).

%%%% For methods
\bibitem{Reidetal:2016}%[Reid et al.(2016)]
Reid, B., Ho, S., \& Padmanabhan, N., et al.  2016, MNRAS, 455, 1553

\bibitem{komatsu2011}%[Komatsu et al.(2011)]
Komatsu, E., Smith, K. M., \& Dunkley, J., et al. 2011, ApJS, 192, 18

\bibitem{hong2016}%[Hong et al.(2016)]
Hong, S.E., Park, C.,\&  Kim, J. 2016, ApJ, 823, 103

\bibitem{MDPATCHY}%[Kitaura et al.(2015)]
Kitaura, F.S., Rodriguez-Torres, S., Chuang, C.-H., et al.2016, MNRAS, 456, 4156

\bibitem{Hartlap}%[Hartlap et al.(2006)]
Hartlap J., Simon P. \& Schneider P. [astro-ph/0608064].

\bibitem{Percival2014}%[Percival et al.(2014)]
Percival, W.J., Ross, A.J., \& S\'{a}nchez, A.G., et al. 2014, MNRAS, 439, 2531
